The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-04-09 docs/language_constraint_conll.tex
Noah

\begin{document}
\maketitle
\begin{abstract}
A writer's style depends not just on personal traits but also on her intent and mental state.
In this paper, we show how variants of the same writing task can lead to measurable differences in writing style.
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016},
where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints. clarify}}
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a simple linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
\roy{In addition, our style-based classifier's performance on the story cloze challenge is comparable to state-of-the-art results.} 
%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}

@@

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by personal factors such as age and gender \cite{Schler:2006}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purpose of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}}

@@

The ROC story corpus consists of 49,255 five-sentence commonsense
stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
  an additional 53K stories were released, which results in roughly
  100K stories.}
Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
which resulted in a wide range of different topics.

@@

The goal of this paper is to determine the extent to which 
%does constraining authors in their writing assignments lead to them adopting different writing styles. 
different writing constraints lead the authors to adopt different writing styles. 
In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
We describe our model below.

@@

\begin{itemize}
\item\textit{\textbf{Length}.} The number of words in the sentence.
\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1-5
  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We use character $4$-grams.\footnote{\roy{Experiments with $5$-grams on our development set reached similar performance.}}
\end{itemize}

@@

\end{tabular}
\end{center}
\caption{\label{exp1_features}
The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
along with their frequency in our story cloze training set.
}
\end{table}

@@

Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions  can help alleviate the effects of writing style found in this paper.

>>>>

\begin{document}
\maketitle
\begin{abstract}
A writer's style depends not just on personal traits but also on her intent and mental state.
In this paper, we show how variants of the same writing task can lead to measurable differences in writing style.
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016},
where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints. clarify}}
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a simple linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
\roy{In addition, our style-based classifier's performance on the story cloze challenge is comparable to state-of-the-art results.} 
%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}

@@

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by personal factors such as age and gender \cite{Schler:2006}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purposes of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}}

@@

The ROC story corpus consists of 49,255 five-sentence 
stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
  an additional 53K stories were released, which results in roughly
  100K stories.}
Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
which resulted in a wide range of different topics.

@@

To what extent do
 %does constraining authors in their writing assignments lead to them adopting different writing styles. 
different writing constraints lead authors to adopt different writing styles?
In order to answer this question, we first use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
We describe our model below.

@@

\begin{itemize}
\item\textit{\textbf{Length}:} the number of words in the sentence.
\item\textit{\textbf{Word $n$-grams:}} we use sequences of 1-5
  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
\item\textit{\textbf{Character $n$-grams:}} character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
We use character $4$-grams.\footnote{\roy{Experiments with $5$-grams on our development set reached similar performance.}}
\end{itemize}

@@

\end{tabular}
\end{center}
\caption{\label{exp1_features}
The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
along with their frequencies in our story cloze training set.
}
\end{table}

@@

Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions may help alleviate the effects of writing style found in this paper.

### 2017-04-09 docs/language_constraint_emnlp.tex
Noah

\begin{document}
\maketitle
\begin{abstract}
A writer's style depends not just on personal traits but also on her intent and mental state.
In this paper, we show how variants of the same writing task can lead to measurable differences in writing style.
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016},
where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints. clarify}}
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a  linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
\roy{In addition, our style-based classifier performs on a par with state-of-the-art models on the story cloze task.} 
%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}

@@

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by personal factors such as age and gender \cite{Schler:2006}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} like sentiment \cite{Davidov:2010}\shortv{, sarcasm \cite{Tsur:2010},} and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, as
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purpose of this paper, \emph{style} is defined as content-agnostic writing characteristics, e.g., sentence length.}}

@@

\shortv{While the story cloze task was originally designed to be a story understanding challenge, }
Interestingly, the story cloze task annotation process introduced three different variants of the writing task of writing an ending to a short story (\secref{ROC_Story}).
In this paper, we show that a linear classifier informed with stylistic features can distinguish among these endings to a large degree, even without looking at the rest of the story\shortv{ (64.5--68.5\% binary classification results)}.

@@

\isubsection{Background: The Story Cloze Task}{ROC_Story}
To understand how different writing tasks affect writing style, 
we focus on the \textit{story cloze task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense story understanding,
its design included a few key choices which  make it ideal for our study. 
We describe the task below.

@@

The ROC story corpus consists of 49,255 five-sentence commonsense
stories, collected on Amazon Mechanical Turk (AMT).\shortv{\footnote{Recently,
  an additional 53K stories were released, which results in roughly
  100K stories.}}
Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
\shortv{To collect a broad spectrum of commonsense knowledge,  n}No subject was imposed for the stories,
which resulted in a wide range of different topics.

@@

The goal of this paper is to determine the extent to which 
%does constraining authors in their writing assignments lead to them adopting different writing styles. 
different writing constraints lead the authors to adopt different writing styles. 
In order to answer these questions, we use simple methods that do not capture content, and have been shown to be effective for recognizing style\shortv{ (see \secref{Related})}.
\shortv{We describe our model below.}

We train a logistic regression classifier to categorize an ending,
either as {\it right} vs.~{\it wrong} or as {\it original} vs.~new ({\it right}).
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features: (a) \textit{\textbf{Length}.} The number of words in the sentence, 
(b) \textit{\textbf{Word $n$-grams.}} Sequences of 1-5
  words,\footnote{In order to focus on style, we replace content words (nouns, verbs, adjectives, and adverbs) with their POS tags.}
and (c) \textit{\textbf{Character $n$-grams.}} \roy{Sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}

@@

\end{tabular}
\end{center}
\caption{\label{exp1_features}
The top 3 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
along with their feature weight (Wt.)~and their frequency in our story cloze training set (Freq.).
}
\end{table}

@@

Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
While this is partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), our findings also indicate that simple instructions  can help alleviate the effects of writing style found in this paper.
\shortv{One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.}

>>>>

\begin{document}
\maketitle
\begin{abstract}
A writer's style depends not just on personal traits but also on her intent and mental state.
In this paper, we show how variants of the same writing task can lead to measurable differences in writing style.
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016},
where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints. clarify}}
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a  linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
\roy{In addition, our style-based classifier performs on a par with state-of-the-art models on the story cloze task.} 
%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}

@@

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by personal factors such as age and gender \cite{Schler:2006}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} like sentiment \cite{Davidov:2010}\shortv{, sarcasm \cite{Tsur:2010},} and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, as
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purposes of this paper, \emph{style} is defined as content-agnostic writing characteristics, e.g., sentence length.}}

@@

\shortv{While the story cloze task was originally designed to be a story understanding challenge, }
Interestingly, the story cloze task annotation process introduced three different variants of the task of writing an ending to a short story (\secref{ROC_Story}).
In this paper, we show that a linear classifier informed with stylistic features can distinguish among these endings to a large degree, even without looking at the rest of the story\shortv{ (64.5--68.5\% binary classification results)}.

@@

\isection{Background: The Story Cloze Task}{ROC_Story}
To understand how different writing tasks affect writing style, 
we focus on the \textit{story cloze task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense story understanding,
its design included a few key choices which  make it ideal for our study. 
We describe the task below.

@@

The ROC story corpus consists of 49,255 five-sentence 
stories, collected on Amazon Mechanical Turk (AMT).\shortv{\footnote{Recently,
  an additional 53K stories were released, which results in roughly
  100K stories.}}
Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
\shortv{To collect a broad spectrum of commonsense knowledge,  n}No subject was imposed for the stories,
which resulted in a wide range of different topics.

@@

To what extent do
%does constraining authors in their writing assignments lead to them adopting different writing styles. 
different writing constraints lead authors to adopt different writing styles?
In order to answer this question, we first use simple methods that do not capture content, and have been shown to be effective for recognizing style\shortv{ (see \secref{Related})}.
\shortv{We describe our model below.}

We train a logistic regression classifier to categorize an ending,
either as {\it right} vs.~{\it wrong} or as {\it original} vs.~new ({\it right}).
Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
We use the following style features: (a) \textit{\textbf{Length}:} the number of words in the sentence;
(b) \textit{\textbf{Word $n$-grams:}} sequences of 1-5
  words;\footnote{In order to focus on style, we replace content words (nouns, verbs, adjectives, and adverbs) with their POS tags.}
and (c) \textit{\textbf{Character $n$-grams:}} \roy{sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}

@@

\end{tabular}
\end{center}
\caption{\label{exp1_features}
The top 3 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
along with their weights (Wt.)~and their frequencies in our story cloze training set (Freq.).
}
\end{table}

@@

Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
While this is partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), our findings also indicate that simple instructions  may help alleviate the effects of writing style found in this paper.
\shortv{One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.}
